Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-07-16 tex/Main Text/manuscript.tex
可以调用synth方法进行分析的版本
结果第一段写完

%tag 结果
\section*{Results}
\subsection*{Division of Water Utilization Regimes}
% 这一节主要展示BCDI的变化趋势和WUR的划分
Figure \ref{fig:wcci} shows the change trend of the index.

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:wcci}
\end{figure}

\subsection*{Drivers of the First Regime Shift}

\subsection*{Drivers of the Second Regime Shift}

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:wcci}
\end{figure}

>>>>

\section*{Results}
%tag 结果1: 指数划分结构
\subsection*{Water utilization regimes}
% 这一节主要展示BCDI的变化趋势和WUR的划分
By the two significantly detected change points,
the changes of IWRU index are split into three periods, 
whose slopes are various and mainly contributed by different factors \ref{fig:IWRU}.
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
and the lightening of water stresses made the most striking contribution (xx\%), 
while tendentiousness and pattern of the water utilization had slight negative contribution.
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
despite positive contributions of tendentiousness and pattern of water utilization,
because of increasing stresses on water resource playing a larger negative role (xx\%). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总的来说，用水三个维度的组合呈现出阶段特征明显，但缓慢过渡的变化趋势
Taken together, combining the three dimensions of water resources utilization, 
whose regimes have clear phase-characteristics with gradual transitions between different phases}.

%tag 结果2
\subsection*{Changes between different regimes}

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:changes}
\end{figure}

\subsection*{Main drivers of the regime shifts}

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:framework}
\end{figure}
